Influences of GDP in the U.S

### 2022-11-14 Manuscript/manuscript.tex
commit

\section*{Abstract}

>>>>

\section*{Abstract}
This study makes an attempt to determine the influence of specific economic factors namely Population, Business Sector Labor Productivity, 10 Year Treasury Constant Maturity Rate, Disposable Personal Income, Unemployment Rate, and Total Primary Energy Consumption on United States GDP.
The data is collected from Federal Reserve Bank of St. Louis  and the U.S. Energy Information Administration from the period of January 1st, 1973 to July 1st, 2022. 
This study’s scope is limited to these listed variables. 
Ordinary Least Squares Regression is used to analyze the relationship between GDP and these variables. 
The main variable of interest is Total Primary Energy Consumption. 
The study revealed that Business Sector Labor Productivity, 10 Year Treasury Constant Maturity Rate, Disposable Personal Income, and Unemployment Rateare factors that significantly predict GDP of the United States.
There was no significant relationship shown between Total Primary Energy Consumption and GDP in the United States based off of this study.
